\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{dirtytalk}

\Large{\title{\textbf{Proof of Concept}}}
\author{Bree Kelly} \date{}

\begin{document}

\maketitle

\paragraph{} ~\\ \large
\noindent{\textbf{Design}}
\paragraph{} ~\\ \noindent
\underline{User Stories}
\paragraph{} ~\\ \noindent
1. As a student of Egyptology, I want to be able to have the program provide a translation of the hieroglyphic text, so that I can save time and focus on the deeper meanings within the text.
\newline \break \noindent
As a student of Egyptology, I should be able to: 1) Operate the program on my device. 2) Provide the program with a readable image of hieroglyphic text. 3) Open the images uploaded into the program. 4) Generate a readable facsimile. 5) Have the program identify hieroglyphic signs and phrases. 6) Have the program produce a transliteration. 7) Have the program produce a translation.
\paragraph{} ~\\ \noindent
1a. As a student of Egyptology, I want to be able to input an image of hieroglyphic text into a program, so that I can have a computer help me translate it.
\newline \break \noindent
As a student of Egyptology, I should be able to: 1) Operate the program on my device. 2) Supply the program with readable image files. 3) Open files uploaded into the program.
\paragraph{} ~\\ \noindent
1b. As a student of Egyptology, I want to be able to create a facsimile from an uploaded image of hieroglyphic text, so that it can be interpreted by the computer.
\newline \break \noindent
As a student of Egyptology, I should be able to: 1) Use a tool within the program to pull the lines of the hieroglyphs out of the background of the image. 2) Use a tool within the program to clean up the facsimile.
\paragraph{} ~\\ \noindent
1c. As a student of Egyptology, I want to be able to have the program identify hieroglyphic signs, so that they can be classified.
\newline \break \noindent
As a student of Egyptology, I should be able to: 1) Select a phrase or word. 2) Organise words and phrases into sentences. 3) Auto-classify (and manually classify, where needed) individual signs. 4) Auto-classify (and manually classify, where needed) sign groupings (such as cartouches).
\paragraph{} ~\\ \noindent
1d. As a student of Egyptology, I want to be able to translate hieroglyphic signs, so that I can produce a translated sentence.
\newline \break \noindent
As a student of Egyptology, I should be able to: 1) Have the program provide a transliteration. 2) Have the program provide a translation.

\end{document}